---
title: "JewelBeetlesMidIRScript1"
output: html_document
date: "2024-04-18"
editor_options: 
  chunk_output_type: console
---

# Libraries

```{r}
install.packages("pavo")
install.packages("ggplot2")
install.packages("dplyr")
install.packages("tidyr")
install.packages("dplyr")
install.packages("stringr")
install.packages("DescTools")
install.packages("ggrepel")
install.packages("ggExtra")

```


```{r}
library(pavo)
library(ggplot2)
library(dplyr)
library(tidyr)
library(dplyr)
library(stringr)
library(DescTools)
library(ggrepel)
library(ggExtra)
```

# Functions

## Import data

The following function imports the model data directly from the folder path. Each folder corresponds to one of the experiments detailed above.

```{r}
import_dpt_files <- function(directory) {
  # Get a list of all files in the directory
  all_files <- list.files(directory, full.names = TRUE)
  
  # Filter files based on the .dpt extension
  file_list <- all_files[grepl("\\.dpt$", all_files)]
  
  # Initialize an empty list to store data frames
  data_list <- list()
  
  # Loop through each file, read it, add column names, and append to data_list
  for (file in file_list) {
    data <- read.table(file, header = FALSE, sep = "\t")  # No header
    colnames(data) <- c("wavenumber", "percent")  # Add column names
    # Add a new column with the file name
    data$filename <- basename(file)
    data_list[[length(data_list) + 1]] <- data
  }
  
  # Ensure all data frames have the same column names
  consistent_data <- lapply(data_list, function(df) {
    colnames(df) <- c("wavenumber", "percent", "filename")  # Reassign col names 
    return(df)
  })
  
  # Combine all data frames in data_list into one master data frame
  master_df <- do.call(rbind, consistent_data)
  
  # Optional: You may want to reset row names if needed
  rownames(master_df) <- NULL
  
  return(master_df)
}

```


## Fix file names

Use this function only if file names need to be fixed. I used to unify the transmittance measurements


```{r eval=FALSE}
add_suffix_to_filenames <- function(directory, old_string, new_string) {
  # Get a list of all files in the directory
  all_files <- list.files(directory, full.names = TRUE)
  
  # Loop through each file and rename it by substituting the old_string with new_string
  for (file in all_files) {
    # Get the file name without the path
    filename <- basename(file)
    
    # Check if the old_string is in the filename
    if (grepl(old_string, filename)) {
      # Replace old_string with new_string in the filename
      new_filename <- gsub(old_string, new_string, filename)
      
      # Construct the new full file path
      new_filepath <- file.path(directory, new_filename)
      
      # Rename the file
      file.rename(file, new_filepath)
    }
  }
}

# Usage example
directory <- "Data/midIR/mirIRTransmittanceMicroscope"
old_string <- ""
new_string <- ""
add_suffix_to_filenames(directory, old_string, new_string)

```


## Smooth curves

This function is needed because the analysis requires the multiplication fo two curves that do not vary in intervals of the same size. 

```{r}

# Function to smooth curves with specified wavelength range and interval size
smooth_curve <- function(data, interval_size, min_wavelength, max_wavelength) {
  # Extract wavelength and radiance from the data frame
  wavelength <- data[[1]]
  radiance <- data[[2]]
  
  # Generate a sequence of evenly spaced wavelengths within the specified range
  new_wavelength <- seq(min_wavelength, max_wavelength, by = interval_size)
  
  # Interpolate the radiance values at the new wavelengths using spline
  spline_fit <- spline(wavelength, radiance, xout = new_wavelength)
  new_radiance <- round(spline_fit$y, 4)  # Round to 4 decimal places
  
  # Return a data frame with the smoothed wavelength and radiance
  data.frame(wavelength = new_wavelength, radiance = new_radiance)
}

# Main function to apply smoothing to each radiance column
smooth_all_curves <- function(data, interval_size, 
                              min_wavelength, max_wavelength) {
  # Extract wavelength column
  wavelength <- data[[1]]
  
  # Initialize a new data frame with the new wavelengths
  new_wavelength <- seq(min_wavelength, max_wavelength, by = interval_size)
  smoothed_data <- data.frame(wavelength = new_wavelength)
  
  # Loop through each radiance column and apply the smoothing function
  for (col in names(data)[-1]) {
    radiance <- data[[col]]
    smoothed_result <- smooth_curve(data.frame(wavelength, radiance), 
                                    interval_size, 
                                    min_wavelength, max_wavelength)
    smoothed_data[[col]] <- round(smoothed_result$radiance, 4)# 4 decimal places
  }
  
  return(smoothed_data)
}

```

## Weighted measurements

Use this function to find the multiplication between any experimental measurement and a given black body radiation data. It assumes that the black body radiation is in a data frame with wavelength in the first column and radiation in the second column. It also assumes that the in the sample data frame, the first column is the wavelength and each fo the columns from 2 onward are different species. Finally, it requires that both data frames have the same number of rows, which is achieved with the previous smoothing functions. 

```{r}
# Define the function to calculate the product of radiance and transmittance
multiply_sample_bb <- function(radiance_df, transmittance_df) {
  # Extract the radiance column
  radiance <- radiance_df[, 2]
  
  # Initialize an empty data frame to store the results
  Result <- data.frame(wavelength = transmittance_df[, 1])
  
  # Loop through each transmittance column (> 2nd column)
  for (i in 2:ncol(transmittance_df)) {
    # Multiply radiance with the current transmittance column
    product <- radiance * transmittance_df[, i]
    
    # Add the result as a new column in the results data frame
    # Use the name of the current transmittance column
    Result[[names(transmittance_df)[i]]] <- product
  }
  
  # Return the resulting data frame
  return(Result)
}

```

## Area under the curve

This function is used to calculate the are under the curve of a weighted measurement, i.e. reflectance or transmittance that has been multiplied by the black body radiation.

```{r}

# using the AUC function from DescTools
calculate_auc <- function(df) {
  # Extract the wavelength column
  wavelength <- df[, 1]
  
  # Initialize a named vector to store the AUC for each species
  auc_values <- numeric(ncol(df) - 1)
  names(auc_values) <- names(df)[-1]
  
  # Loop through each species column (2 onwards)
  for (i in 2:ncol(df)) {
    # Extract the current species column
    weighteddata <- df[, i]
    
    # Calculate the area under the curve using the AUC function
    auc_value <- AUC(wavelength, weighteddata)
    
    # Store the AUC value in the auc_values vector
    auc_values[i - 1] <- auc_value
  }
  
  # Return the auc_values vector
  return(auc_values)
}

```

# Raw data

## ViS-NIR

### Hemispherical reflectance

```{r}
Jdat0 <-  read.csv("Data/VIS_NIR/JewelHemisphericalRefCompiled.csv")

# Filter out the raw current values
Jdat <- Jdat0 %>% 
  select(ends_with("_cal"))# keep only calibrated values 
  
names(Jdat) <- substr(names(Jdat),5,31)
  
Jdat$wl <- Jdat0$wl1 # add wavelentgh column

JdatR <- Jdat %>% 
  select(sort(names(.))) %>% 
  select(wl,everything()) %>%
  gather(key= "sample" , value= "reflectance", -wl) %>% 
  mutate("treat" = substr(sample, 1,21)) %>% 
  group_by(treat,wl) %>% 
  summarise("avReflect" =  mean(reflectance),
            "sdreflect" = sd(reflectance)) %>% 
  mutate("spot" = substr(treat, 9,21),
         "spp" =  substr(treat,1,7))


head(JdatR)

```

General plot: 

```{r}
ggplot(JdatR, aes(x=wl,y=avReflect,color=spot)) +
  geom_line()+
  xlim(420,1100)+
  ylim(0,60)+
  ylab("Reflectance (%)")+
  xlab("Wavelength (nm)")+
  facet_wrap(~spp)+
  theme_bw()

```


### Transmittance

```{r}
Jdat0.1 <-  read.csv("Data/VIS_NIR/JewelTransmittanceCompiled.csv")

# Filter out the raw current values
Jdat1 <- Jdat0.1 %>% 
  select_if(~sum(!is.na(.)) > 0) %>% 
  select(ends_with("_cal"))# keep only calibrated values 
  
names(Jdat1) <- substr(names(Jdat1),5,34)
  
Jdat1$wl <- Jdat0.1$wl1 # add wavelentgh column

JdatT <- Jdat1 %>% 
  select(sort(names(.))) %>% 
  select(wl,everything()) %>%
  gather(key= "sample" , value= "transmittance", -wl) %>% 
  mutate("spot" = substr(sample, 9,21),
         "spp" =  substr(sample,1,7)
         ) %>% 
  group_by(spp,spot,wl) %>% 
  summarise("avTrans" =  mean(transmittance),
            "sdTrans" = sd(transmittance)) 


head(JdatT)

```

General plot: 

```{r}
ggplot(JdatT, aes(x=wl,y=avTrans,color=spot)) +
  geom_line()+
  xlim(420,1100)+
  ylim(0,85)+
  ylab("Transmittance (%)")+
  xlab("Wavelength (nm)")+
  facet_wrap(~spp)+
  theme_bw()

```

## Sun Irradiance

```{r}
SunRaw <- read.csv("Data/RawSun/SolarIrradiance.csv") 
```

To make sure that the sun irradiance and samples are in the same wavelength range (400 - 1100 nm) and the wavelength varies in steps of the same size (0.1 nanometers), we use the function "smooth curve" set in the "functions" section of this document. 

And we define the parameters for vis nir (these will change for midIR).

```{r}
#Parameters for vis nir
interval_sizeVN <- 0.1
min_wavelengthVN <- 420
max_wavelengthVN <- 1100

smoo_sun <- smooth_curve(SunRaw, interval_sizeVN, 
                             min_wavelengthVN, max_wavelengthVN)

length(smoo_sun$wavelength)

plot(smoo_sun, type="l")

```


## midIR

hemispherical reflectance of long wavelengths was measured with a gold covered integrating sphere. Transmittance was measured with the microscope (no lenses, mirror objectives).


### Reflectance 

import and clean data. Use the function to import data set at the begining of this document.

```{r}
directory1 <- "Data/midIR/mirIRHemisphericalReflectance"
master_df2 <- import_dpt_files(directory1)
head(master_df2)
```

arrange data frame and get the mean across the repetitions.

```{r}

midirRef <- master_df2 %>% 
  mutate(wl = 10000/wavenumber, # calculate wavelength (x axis)
         spp = substr(filename, 1,6), # species
         spot = substr(filename, 8, 12) # different spots
         ) %>% 
  select(spp,spot, wl,percent) %>% 
  group_by(spp, spot, wl) %>% 
  summarise(meanRef = mean(percent), # average across repetitions
            sdRef = sd(percent), # sd accross repetitions
            nRef = length(percent))

head(midirRef)

```

#### Plot elytra

First subset by elytra
```{r}
ReflElDor <- midirRef %>% 
  filter(spot == "ElDor")

ggplot(ReflElDor, aes(x=wl, y=meanRef, group = spp, col=spp))+
  geom_line()+
  theme_bw()
```

#### Plot body parts

```{r}

ReflWA <- midirRef %>% 
  filter(spp == "Tbruck" | 
         spp == "Tbonvo") 

head(ReflWA)
table(ReflWA$spot)

ggplot(ReflWA, aes(x=wl, y=meanRef, col=spot))+
  geom_line()+
  facet_wrap(~spp)+
  theme_bw()

```


### Transmittance

Import data

```{r}
directory3 <- "Data/midIR/mirIRTransmittanceMicroscope"
master_df3 <- import_dpt_files(directory3)
head(master_df3)
```

Arrange data frame

```{r}

midirTra <- master_df3 %>% 
  mutate(wl = 10000/wavenumber, # conver wave number to wavelength
         spp = substr(filename, 1,6), # species
         spot = substr(filename, 8,12)# separate by spot
         ) %>% 
  select(spp,spot, wl,percent) %>% 
  group_by(spp, spot, wl) %>% 
  summarise(meanTra = mean(percent), 
            sdTra = sd(percent),
            nTra = length(percent))

head(midirTra)
unique(midirTra$spot)

```


#### Plot elytra

First subset by elytra
```{r}
TrElytraDor <- midirTra %>% 
  filter(spot == "ElDor")
summary(TrElytraDor)

TrElytraVen <- midirTra %>% 
  filter(spot == "ElVen")

TrRightWing <- midirTra %>% 
  filter(spot == "RWing")


ggplot(TrElytraDor, aes(x=wl, y=meanTra, col=spp))+
  geom_ribbon(aes(ymin = meanTra - sdTra, 
                  ymax = meanTra + sdTra, 
                  group = spp, fill = spp),
              alpha = 0.4, colour = NA) +
  geom_line()+
  theme_bw()

ggplot(TrElytraVen, aes(x=wl, y=meanTra, col=spp))+
  geom_ribbon(aes(ymin = meanTra - sdTra, 
                  ymax = meanTra + sdTra, 
                  group = spp, fill = spp),
              alpha = 0.4, colour = NA) +
  geom_line()+
  theme_bw()


ggplot(TrRightWing, aes(x=wl, y=meanTra, col=spp))+
  geom_ribbon(aes(ymin = meanTra - sdTra, 
                  ymax = meanTra + sdTra, 
                  group = spp, fill = spp),
              alpha = 0.4, colour = NA) +
  geom_line()+
  theme_bw()

```


notes: ** if the elytron does not contain a lot of living tissue, maybe it does not need to dissipate heat, that would explain higer transmittance. Would this be the case of E. lamp?

Or is it due to the thickness of the chiral stack??? or maybe due to roughness???



#### Plot Elytral chamber

```{r}
TranWA <- midirTra %>% 
  filter(spp == "Tbruck" | 
         spp == "Tbonvo") 

head(TranWA)

ggplot(TranWA, aes(x=wl, y=meanTra, col=spot))+
  geom_ribbon(aes(ymin = meanTra - sdTra, 
                  ymax = meanTra + sdTra, 
                  group = spot, fill = spot), alpha=0.2, colour=NA)+
  geom_line()+
  theme_bw()+
  facet_wrap(~spp)

```


## Black Body

These files contain a column for wavelength in microns and radiance in photons/s/m2/sr/micron.

```{r}
directory5 <-"Data/RawBlackBody"
```

```{r}

# import data
Temp293<-read.table("Data/RawBlackBody/Temp293K.txt",header=TRUE) %>% 
  filter(wavelength>=3)# 19.85C
Temp300<-read.table("Data/RawBlackBody/Temp300K.txt",header=TRUE) %>% 
  filter(wavelength>=3)# 26.85C
Temp321<-read.table("Data/RawBlackBody/Temp321K.txt",header=TRUE) %>% 
  filter(wavelength>=3)# 47.85
Temp333<-read.table("Data/RawBlackBody/Temp333K.txt",header=TRUE) %>% 
  filter(wavelength>=3)# 59.85
Temp343<-read.table("Data/RawBlackBody/Temp343K.txt",header=TRUE) %>% 
  filter(wavelength>=3)# 69.85

plot(Temp343,type="l")
lines(Temp333, col="green")
lines(Temp321, col="pink")
lines(Temp300, col="red")
lines(Temp293, col="blue")

```

To make sure that the black body radiation and samples are in the same wavelength range (3 - 16 microns) and the wavelength varies in steps of the same size (0.0001 microns), we use the function "smooth curve" set in the "functions" section of this document.


```{r}
#Parameters for midIR
interval_size <- 0.0001
min_wavelength <- 3
max_wavelength <- 16

smoo_Temp293 <- smooth_curve(Temp293, interval_size, 
                             min_wavelength, max_wavelength)
smoo_Temp300 <- smooth_curve(Temp300, interval_size, 
                             min_wavelength, max_wavelength)
smoo_Temp321 <- smooth_curve(Temp321, interval_size, 
                             min_wavelength, max_wavelength)
smoo_Temp333 <- smooth_curve(Temp333, interval_size, 
                             min_wavelength, max_wavelength)
smoo_Temp343 <- smooth_curve(Temp343, interval_size, 
                             min_wavelength, max_wavelength)

```

To confirm: 

```{r}
summary(smoo_Temp343)
length(smoo_Temp343$wavelength)
```

# Weighted Data

## VIs-NIR Transmission


##### Step 1 - Setting up

We used the function smooth_all_curves to make sure that the transmittance data is in the same wavelength range (400 ) and the wavelength varies in steps of the same size (0.0001 microns). This function is required to apply the smoothing in multiple columns of a data frame all at once. 

```{r}

TrJdat.SP <- JdatT %>%
  ungroup() %>% 
  unite("treat", spp, spot, sep ="_") %>% 
  select(treat,wl,avTrans) %>% 
  spread(treat,avTrans) %>% 
  filter(wl>=420)

smoo_TrJdat <- smooth_all_curves(TrJdat.SP, interval_sizeVN, 
                             min_wavelengthVN, max_wavelengthVN)

head(TrJdat.SP)
head(smoo_TrJdat)
length(smoo_TrJdat$wavelength)

```

##### Step 2 -  multiplication

Multiply the sample transmittance * sun irradiance. In order to do this, use the function "multiply_sample_bb"

```{r}
TrJdatSun <- multiply_sample_bb(smoo_sun, smoo_TrJdat)
head(TrJdatSun)
```

This is the comparison of the raw and weighted data for A. aureus: 
```{r}
par(mfrow=c(1,2))
plot(smoo_TrJdat[,1:2], type="l", ylab= "Raw transmittance")
plot(TrJdatSun[,1:2], type="l", ylab= "Weighted transmittance")
```

##### Step 3 -  Integral

We use the function "area under the curve" to calculate the integral under the weighted curve.
```{r}
Transmissivity <- calculate_auc(TrJdatSun)/calculate_auc(smoo_sun)
Transmissivity
```



## VIS-NIR Reflection


##### Step 1 - Setting up

We used the function smooth_all_curves to make sure that the transmittance data is in the same wavelength range (400 ) and the wavelength varies in steps of the same size (0.0001 microns). This function is required to apply the smoothing in multiple columns of a data frame all at once. 

```{r}

RfJdat.SP <- JdatR %>%
  ungroup() %>% 
  select(treat,wl,avReflect) %>% 
  spread(treat,avReflect) %>% 
  filter(wl>=420)

smoo_RfJdat <- smooth_all_curves(RfJdat.SP, interval_sizeVN, 
                             min_wavelengthVN, max_wavelengthVN)

head(RfJdat.SP)
head(smoo_RfJdat)
length(smoo_RfJdat$wavelength)

```

##### Step 2 -  multiplication

Multiply the sample transmittance * sun irradiance. In order to do this, use the function "multiply_sample_bb"

```{r}
RfJdatSun <- multiply_sample_bb(smoo_sun, smoo_RfJdat)
head(RfJdatSun)
```

This is the comparison of the raw and weighted data for A. aureus: 
```{r}
par(mfrow=c(1,2))
plot(smoo_RfJdat[,1:2], type="l", ylab= "Raw reflectance")
plot(RfJdatSun[,1:2], type="l", ylab= "Weighted reflectance")
```

##### Step 3 -  Integral

We use the function "area under the curve" to calculate the integral under the weighted curve.
```{r}
Reflectivity <- calculate_auc(RfJdatSun)/calculate_auc(smoo_sun)
Reflectivity
```






## IR transmission

### Elytra Dorsal

##### Step 1 - Setting up

We used the function smooth_all_curves to make sure that the transmittance data is in the same wavelength range (3 - 16 microns) and the wavelength varies in steps of the same size (0.0001 microns). This function is required to apply the smoothing in multiple columns of a data frame all at once. 

```{r}
TrElytraDor.SP <- TrElytraDor %>%
  ungroup() %>% 
  select(spp,wl,meanTra) %>% 
  spread(spp,meanTra) %>% 
  filter(wl>=3)

smoo_TrElytraDor <- smooth_all_curves(TrElytraDor.SP, interval_size, 
                             min_wavelength, max_wavelength)
 
```

To confirm:
```{r}
summary(smoo_TrElytraDor$wavelength) 
length(smoo_TrElytraDor$wavelength)
```

##### Step 2 -  multiplication

Multiply the sample transmittance * black body radiation at a given temperature. In order to do this, use the function "multiply_sample_bb"

```{r}
Tr.Ely.300bb <- multiply_sample_bb(smoo_Temp300, smoo_TrElytraDor)
head(Tr.Ely.300bb)
```

This is the comparison of the raw and weighted data for A. aureus: 
```{r}
par(mfrow=c(1,2))
plot(smoo_TrElytraDor[,1:2], type="l", ylab= "Raw transmittance")
plot(Tr.Ely.300bb[,1:2], type="l", ylab= "Weighted transmittance")
```

Now, multiply for the black body radiation at different temperatures: 

```{r}
Tr.Ely.293bb <- multiply_sample_bb(smoo_Temp293, smoo_TrElytraDor)
Tr.Ely.300bb <- multiply_sample_bb(smoo_Temp300, smoo_TrElytraDor)
Tr.Ely.321bb <- multiply_sample_bb(smoo_Temp321, smoo_TrElytraDor)
Tr.Ely.333bb <- multiply_sample_bb(smoo_Temp333, smoo_TrElytraDor)
Tr.Ely.343bb <- multiply_sample_bb(smoo_Temp343, smoo_TrElytraDor)
```

##### Step 3 -  Integral

We use the function "area under the curve" to calculate the integral under the weighted curve.
```{r}
IRTra_Ely_293bb <- 1-(calculate_auc(Tr.Ely.293bb)/calculate_auc(smoo_Temp293))
IRTra_Ely_300bb <- 1-(calculate_auc(Tr.Ely.300bb)/calculate_auc(smoo_Temp300))
IRTra_Ely_321bb <- 1-(calculate_auc(Tr.Ely.321bb)/calculate_auc(smoo_Temp321))
IRTra_Ely_333bb <- 1-(calculate_auc(Tr.Ely.333bb)/calculate_auc(smoo_Temp333))
IRTra_Ely_343bb <- 1-(calculate_auc(Tr.Ely.343bb)/calculate_auc(smoo_Temp343))
```

##### Step 4 - plot

```{r}
IRTr = c(IRTra_Ely_293bb, IRTra_Ely_300bb, IRTra_Ely_321bb, 
         IRTra_Ely_333bb, IRTra_Ely_343bb)

IRTra_Ely_pivot <- data.frame(
  species = names(IRTr),
  value = as.numeric(IRTr),
  bbTemp = substr(
    c(rep("IRTra_Ely_293bb",length(IRTra_Ely_293bb)), 
             rep("IRTra_Ely_300bb",length(IRTra_Ely_300bb)), 
             rep("IRTra_Ely_321bb",length(IRTra_Ely_321bb)), 
             rep("IRTra_Ely_333bb",length(IRTra_Ely_333bb)),
             rep("IRTra_Ely_343bb",length(IRTra_Ely_343bb))),
    11,15)
)

ggplot(IRTra_Ely_pivot, aes(fill=bbTemp, y=value, x=species)) + 
  geom_bar(position="dodge", stat="identity")+
  ylim(0,1)+
  theme_bw()

new_labels <- c("293K | 19.8C", 
                "300K | 26.8C", 
                "321K | 47.8C", 
                "333K | 59.8C", 
                "343K | 69.8C")

ggplot(IRTra_Ely_pivot, aes(x=bbTemp, y=value))+
  geom_boxplot(fill="pink")+
  geom_point(aes(y=value), cex=3, pch=21)+
  geom_text_repel(aes(label = species), size = 3) + # Add species names as labels
  scale_x_discrete(labels = new_labels) +  # Change x-axis labels
  ylab("Calc. Emissivity")+
  theme_bw()


```

Some preliminary stats for one of the outliers: 

```{r}
# Example sample data
sample_data <- IRTra_Ely_pivot[IRTra_Ely_pivot$bbTemp == "293bb",2]

# Specify the single observed value
observed_value <- IRTra_Ely_pivot[IRTra_Ely_pivot$species=="Elampr" 
                       & IRTra_Ely_pivot$bbTemp == "293bb",2]

# Calculate the sample mean and standard deviation
sample_mean <- mean(sample_data)
sample_sd <- sd(sample_data)
n <- length(sample_data)

# Calculate the t-score
t_score <- (observed_value - sample_mean) / (sample_sd / sqrt(n))

# Calculate the p-value for the t-score
p_value <- 2 * pt(-abs(t_score), df = n - 1)

# Print the results
cat("t-score:", t_score, "\n")
cat("p-value:", p_value, "\n")

```


### Elytra Ventral 

##### Step 1 - Setting up

We used the function smooth_all_curves to make sure that the transmittance data is in the same wavelength range (3 - 16 microns) and the wavelength varies in steps of the same size (0.0001 microns). This function is required to apply the smoothing in multiple columns of a data frame all at once. 

```{r}
TrElytraVen.SP <- TrElytraVen %>%
  ungroup() %>% 
  select(spp,wl,meanTra) %>% 
  spread(spp,meanTra) %>% 
  filter(wl>=3)

smoo_TrElytraVen <- smooth_all_curves(TrElytraVen.SP, interval_size, 
                             min_wavelength, max_wavelength)
 
```

To confirm:
```{r}
summary(smoo_TrElytraVen$wavelength) 
length(smoo_TrElytraVen$wavelength)
```

##### Step 2 -  multiplication

Multiply the sample transmittance * black body radiation at a given temperature. In order to do this, use the function "multiply_sample_bb"

```{r}
Tr.ElV.300bb <- multiply_sample_bb(smoo_Temp300, smoo_TrElytraVen)
head(Tr.ElV.300bb)
```

This is the comparison of the raw and weighted data for A. aureus: 
```{r}
par(mfrow=c(1,2))
plot(smoo_TrElytraVen[,1:2], type="l", ylab= "Raw transmittance")
plot(Tr.ElV.300bb[,1:2], type="l", ylab= "Weighted transmittance")
```

Now, multiply for the black body radiation at different temperatures: 

```{r}
Tr.ElV.293bb <- multiply_sample_bb(smoo_Temp293, smoo_TrElytraVen)
Tr.ElV.300bb <- multiply_sample_bb(smoo_Temp300, smoo_TrElytraVen)
Tr.ElV.321bb <- multiply_sample_bb(smoo_Temp321, smoo_TrElytraVen)
Tr.ElV.333bb <- multiply_sample_bb(smoo_Temp333, smoo_TrElytraVen)
Tr.ElV.343bb <- multiply_sample_bb(smoo_Temp343, smoo_TrElytraVen)
```

##### Step 3 -  Integral

We use the function "area under the curve" to calculate the integral under the weighted curve.
```{r}
IRTra_ElV_293bb <- 1-(calculate_auc(Tr.ElV.293bb)/calculate_auc(smoo_Temp293))
IRTra_ElV_300bb <- 1-(calculate_auc(Tr.ElV.300bb)/calculate_auc(smoo_Temp300))
IRTra_ElV_321bb <- 1-(calculate_auc(Tr.ElV.321bb)/calculate_auc(smoo_Temp321))
IRTra_ElV_333bb <- 1-(calculate_auc(Tr.ElV.333bb)/calculate_auc(smoo_Temp333))
IRTra_ElV_343bb <- 1-(calculate_auc(Tr.ElV.343bb)/calculate_auc(smoo_Temp343))
```

##### Step 4 -  plot

```{r}
IRTrV = c(IRTra_ElV_293bb, IRTra_ElV_300bb, IRTra_ElV_321bb, 
         IRTra_ElV_333bb, IRTra_ElV_343bb)

IRTra_ElV_pivot <- data.frame(
  species = names(IRTrV),
  value = as.numeric(IRTrV),
  bbTemp = substr(
    c(rep("IRTra_ElV_293bb",length(IRTra_ElV_293bb)), 
             rep("IRTra_ElV_300bb",length(IRTra_ElV_300bb)), 
             rep("IRTra_ElV_321bb",length(IRTra_ElV_321bb)), 
             rep("IRTra_ElV_333bb",length(IRTra_ElV_333bb)),
             rep("IRTra_ElV_343bb",length(IRTra_ElV_343bb))),
    11,15)
)

ggplot(IRTra_ElV_pivot, aes(fill=bbTemp, y=value, x=species)) + 
  geom_bar(position="dodge", stat="identity")+
  ylim(0,1)+
  theme_bw()

new_labels <- c("293K | 19.8C", 
                "300K | 26.8C", 
                "321K | 47.8C", 
                "333K | 59.8C", 
                "343K | 69.8C")

ggplot(IRTra_ElV_pivot, aes(x=bbTemp, y=value))+
  geom_boxplot(fill="pink")+
  geom_point(aes(y=value), cex=3, pch=21)+
  geom_text_repel(aes(label = species), size = 3) + # Add species names as labels
  scale_x_discrete(labels = new_labels) +  # Change x-axis labels
  ylab("Calc. Emissivity")+
  theme_bw()
```


### Dorsal-Ventral comparison

In order to test if there is any difference in the transmittance of the elytra from the dorsal or ventral side.
```{r}
CompEly <- inner_join(IRTra_ElV_pivot, IRTra_Ely_pivot,  
                      by = c("species", "bbTemp")) %>% 
  rename(VentralTr = value.x ,
         DorsalTr = value.y) %>% 
  mutate(Diff = DorsalTr-VentralTr)

# Statistical tests
wilcox.test((CompEly)[CompEly$bbTemp=="293bb",]$Diff,mu=0) # non parametric test used
summary(CompEly$Diff) # descriptive stats

# Create the base scatter plot
p <- ggplot(CompEly, 
            aes(x = VentralTr, y = DorsalTr, group=bbTemp, colour=bbTemp)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  geom_point(pch=16, cex=3) +
  geom_text_repel(aes(label = species), size = 3) + # Add species names as labels
  labs(x = "Ventral Emissivity", y = "Dorsal Emissivity")+
  theme_bw() +
  xlim(0.9,1)+
  ylim(0.9,1)+
  theme(legend.position = "bottom")


# Add marginal histograms
p_with_margins <- ggMarginal(p, type = "histogram", bins = 30, 
                             fill = "skyblue", color = "black")

# Display the plot
print(p_with_margins)

```



### Right Wing


## IR Reflection

### Elytra dorsal


##### Step 1 - Setting up

We used the function smooth_all_curves to make sure that the transmittance data is in the same wavelength range (3 - 16 microns) and the wavelength varies in steps of the same size (0.0001 microns). This function is required to apply the smoothing in multiple columns of a data frame all at once. 

```{r}
ReflElDor.SP <- ReflElDor %>%
  ungroup() %>% 
  select(spp,wl,meanRef) %>% 
  spread(spp,meanRef) %>% 
  filter(wl>=3)

smoo_ReflElDor <- smooth_all_curves(ReflElDor.SP, interval_size, 
                             min_wavelength, max_wavelength)
 
```

To confirm:
```{r}
summary(smoo_ReflElDor$wavelength) 
length(smoo_ReflElDor$wavelength)
```

##### Step 2 -  multiplication

Multiply the sample transmittance * black body radiation at a given temperature. In order to do this, use the function "multiply_sample_bb"

```{r}
Tr.Ely.300bb <- multiply_sample_bb(smoo_Temp300, smoo_ReflElDor)
head(Tr.Ely.300bb)
```

This is the comparison of the raw and weighted data for A. aureus: 
```{r}
par(mfrow=c(1,2))
plot(smoo_ReflElDor[,1:2], type="l", ylab= "Raw reflectance")
plot(Tr.Ely.300bb[,1:2], type="l", ylab= "Weighted reflectance")
```

Now, multiply for the black body radiation at different temperatures: 

```{r}
Rf.Ely.293bb <- multiply_sample_bb(smoo_Temp293, smoo_ReflElDor)
Rf.Ely.300bb <- multiply_sample_bb(smoo_Temp300, smoo_ReflElDor)
Rf.Ely.321bb <- multiply_sample_bb(smoo_Temp321, smoo_ReflElDor)
Rf.Ely.333bb <- multiply_sample_bb(smoo_Temp333, smoo_ReflElDor)
Rf.Ely.343bb <- multiply_sample_bb(smoo_Temp343, smoo_ReflElDor)
```

##### Step 3 -  Integral

We use the function "area under the curve" to calculate the integral under the weighted curve.
```{r}
IRRef_Ely_293bb <- 1-(calculate_auc(Rf.Ely.293bb)/calculate_auc(smoo_Temp293))
IRRef_Ely_300bb <- 1-(calculate_auc(Rf.Ely.300bb)/calculate_auc(smoo_Temp300))
IRRef_Ely_321bb <- 1-(calculate_auc(Rf.Ely.321bb)/calculate_auc(smoo_Temp321))
IRRef_Ely_333bb <- 1-(calculate_auc(Rf.Ely.333bb)/calculate_auc(smoo_Temp333))
IRRef_Ely_343bb <- 1-(calculate_auc(Rf.Ely.343bb)/calculate_auc(smoo_Temp343))
```

##### Step 4 - plot

```{r}
IRRf <- c(IRRef_Ely_293bb, IRRef_Ely_300bb, IRRef_Ely_321bb, 
         IRRef_Ely_333bb, IRRef_Ely_343bb)

IRRef_Ely_pivot <- data.frame(
  species = names(IRRf),
  value = as.numeric(IRRf),
  bbTemp = substr(
    c(rep("IRRef_Ely_293bb",length(IRRef_Ely_293bb)), 
             rep("IRRef_Ely_300bb",length(IRRef_Ely_300bb)), 
             rep("IRRef_Ely_321bb",length(IRRef_Ely_321bb)), 
             rep("IRRef_Ely_333bb",length(IRRef_Ely_333bb)),
             rep("IRRef_Ely_343bb",length(IRRef_Ely_343bb))),
    11,15)
)

ggplot(IRRef_Ely_pivot, aes(fill=bbTemp, y=value, x=species)) + 
  geom_bar(position="dodge", stat="identity")+
  ylim(0,1)+
  theme_bw()

new_labels <- c("293K | 19.8C", 
                "300K | 26.8C", 
                "321K | 47.8C", 
                "333K | 59.8C", 
                "343K | 69.8C")

ggplot(IRRef_Ely_pivot, aes(x=bbTemp, y=value))+
  geom_boxplot(fill="pink")+
  geom_point(aes(y=value), cex=3, pch=21)+
  geom_text_repel(aes(label = species), size = 3) + # Add species names as labels
  scale_x_discrete(labels = new_labels) +  # Change x-axis labels
  theme_bw()


```


### Body Parts WA

##### Step 1 - Setting up

```{r}
ReflWA.SP <- ReflWA %>% 
  ungroup() %>% 
  unite("sppspot", spp:spot) %>% 
  select(sppspot,wl,meanRef) %>% 
  spread(sppspot,meanRef) %>% 
  filter(wl>=3)

smoo_ReflWA<- smooth_all_curves(ReflWA.SP, interval_size, 
                             min_wavelength, max_wavelength)
```

##### Step 2 -  multiplication

Multiply the sample transmittance * black body radiation at a given temperature. In order to do this, use the function "multiply_sample_bb"

```{r}
ReflWA.300bb <- multiply_sample_bb(smoo_Temp300, smoo_ReflWA)
head(ReflWA.300bb)
```

Now, multiply for the black body radiation at different temperatures: 

```{r}
Rf.WA.293bb <- multiply_sample_bb(smoo_Temp293, smoo_ReflWA)
Rf.WA.300bb <- multiply_sample_bb(smoo_Temp300, smoo_ReflWA)
Rf.WA.321bb <- multiply_sample_bb(smoo_Temp321, smoo_ReflWA)
Rf.WA.333bb <- multiply_sample_bb(smoo_Temp333, smoo_ReflWA)
Rf.WA.343bb <- multiply_sample_bb(smoo_Temp343, smoo_ReflWA)
```

##### Step 3 -  Integral

We use the function "area under the curve" to calculate the integral under the weighted curve.
```{r}
IRRef_WA_293bb <- 1-(calculate_auc(Rf.WA.293bb)/calculate_auc(smoo_Temp293))
IRRef_WA_300bb <- 1-(calculate_auc(Rf.WA.300bb)/calculate_auc(smoo_Temp300))
IRRef_WA_321bb <- 1-(calculate_auc(Rf.WA.321bb)/calculate_auc(smoo_Temp321))
IRRef_WA_333bb <- 1-(calculate_auc(Rf.WA.333bb)/calculate_auc(smoo_Temp333))
IRRef_WA_343bb <- 1-(calculate_auc(Rf.WA.343bb)/calculate_auc(smoo_Temp343))
```

##### Step 4 - plot

```{r}
IRRfWA <- c(IRRef_WA_293bb, IRRef_WA_300bb, IRRef_WA_321bb, 
         IRRef_WA_333bb, IRRef_WA_343bb)

IRRef_WA_pivot <- data.frame(
  sppspot = names(IRRfWA),
  value = as.numeric(IRRfWA),
  bbTemp = substr(
    c(rep("IRRef_WA_293bb",length(IRRef_WA_293bb)), 
             rep("IRRef_WA_300bb",length(IRRef_WA_300bb)), 
             rep("IRRef_WA_321bb",length(IRRef_WA_321bb)), 
             rep("IRRef_WA_333bb",length(IRRef_WA_333bb)),
             rep("IRRef_WA_343bb",length(IRRef_WA_343bb))),
    10,14)
) %>% 
  mutate(spp = substr(sppspot,1,6),
         bodypart = substr(sppspot,8,12)) 
  


new_labels <- c("293K | 19.8C", 
                "300K | 26.8C", 
                "321K | 47.8C", 
                "333K | 59.8C", 
                "343K | 69.8C")

ggplot(IRRef_WA_pivot, aes(x=bbTemp, y=value))+
  geom_boxplot(fill="pink")+
  geom_point(aes(y=value), cex=3, pch=21)+
  geom_text_repel(aes(label = bodypart), size = 3) + # Add species names as labels
  scale_x_discrete(labels = new_labels) +  # Change x-axis labels
  facet_wrap(~spp)+
  theme_bw()


```





# Synthesis


## visNIR

```{r}
Absorptivity <- 100 - (Transmissivity  + Reflectivity)

PivotSun <- data.frame (
  sppspot = c(names(Absorptivity),
              names(Transmissivity),
              names(Reflectivity)),
  value = c(as.numeric(Absorptivity),
            as.numeric(Transmissivity),
            as.numeric(Reflectivity)),
  Oprop = c(rep("Absorptivity",length(Absorptivity)),
            rep("Transmissivity", length(Transmissivity)),
            rep("Reflectivity", length(Reflectivity))
            )) %>% 
  mutate(spp = substr(sppspot,1,7),
         spot = substr(sppspot,16,21),
         manip = substr(sppspot, 9, 14)) %>% 
  unite("SppTreat", spp, manip, sep="_", remove=FALSE) %>% 
  select(SppTreat , spot, value, Oprop, manip)


PivotSun$alpha <- ifelse(PivotSun$manip == "alterd", 0.5, 1)

```

Plot

### Bright spots
```{r}
ggplot(PivotSun[PivotSun$spot=="bright",], 
       aes(x = SppTreat,
           y = value, fill = Oprop ,
           alpha = alpha)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Species", y = "Value") +
  scale_fill_manual(values=c( "#4682B4", "#9ACD32","#FFA500"))+
  scale_alpha_identity() +  # Use identity scale for alpha
  coord_flip()+
  theme_minimal()

```


### Dark spots

```{r}

ggplot(PivotSun[PivotSun$spot=="darkpt",], 
       aes(x = SppTreat,
           y = value, fill = Oprop ,
           alpha = alpha)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Species", y = "Value") +
  scale_fill_manual(values=c( "#4682B4", "#FFA500", "#9ACD32"))+
  scale_alpha_identity() +  # Use identity scale for alpha
  coord_flip()+
  theme_minimal()


```


### What wavlenegths?


Only transmittance //  Comparing if there is more change in the visible or NIR part of the spectrum after alteration (scraping of the material below the upper lamination)

```{r}
TransmVIS <- calculate_auc(TrJdatSun[TrJdatSun$wavelength<700,])/       calculate_auc(smoo_sun[smoo_sun$wavelength<700,])

TransmNIR <- calculate_auc(TrJdatSun[TrJdatSun$wavelength>=700,])/       calculate_auc(smoo_sun[smoo_sun$wavelength>=700,])

PivotTransmT <- data.frame (
  sppspot = c(names(TransmVIS),
              names(TransmNIR)),
  value = c(as.numeric(TransmVIS),
            as.numeric(TransmNIR)),
  Band = c(rep("TransmVIS",length(TransmVIS)),
            rep("TransmNIR", length(TransmNIR))
            )) %>% 
  mutate(spp = substr(sppspot,1,7),
         spot = substr(sppspot,16,21),
         manip = substr(sppspot, 9, 14)) %>% 
  unite("SppTreat", spp, manip, sep="_", remove=FALSE) %>% 
  select(SppTreat , spot, value, Band, manip)

PivotTransmT$alpha <- ifelse(PivotTransmT$manip == "alterd", 0.5, 1)


ggplot(PivotTransmT[PivotTransmT$spot=="bright",], 
       aes(x = SppTreat,
           y = value, alpha = alpha)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.5)) +
  labs(x = "Species", y = "Value") +
  scale_fill_manual("#FFA500")+
  scale_alpha_identity() +  # Use identity scale for alpha
  facet_wrap(~Band)+
  coord_flip()+
  theme_minimal()


```


Full properties//  Comparing if there is more change in the visible or NIR part of the spectrum after alteration (scraping of the material below the upper lamination)

```{r}
ReflecVIS <- calculate_auc(RfJdatSun[RfJdatSun$wavelength<700,])/       calculate_auc(smoo_sun[smoo_sun$wavelength<700,])

ReflecNIR <- calculate_auc(RfJdatSun[RfJdatSun$wavelength>=700,])/       calculate_auc(smoo_sun[smoo_sun$wavelength>=700,])

AbsorbVIS <- 100 - (ReflecVIS + TransmVIS)
AbsorbNIR <- 100 - (ReflecNIR + TransmNIR)

PivotBands <- data.frame (
  sppspot = c(names(AbsorbVIS),
              names(TransmVIS),
              names(ReflecVIS),
              names(AbsorbNIR),
              names(TransmNIR),
              names(ReflecNIR)),
  value = c(as.numeric(AbsorbVIS),
            as.numeric(TransmVIS),
            as.numeric(ReflecVIS),
            as.numeric(AbsorbNIR),
            as.numeric(TransmNIR),
            as.numeric(ReflecNIR)),
  Oprop = c(rep("AbsorbVIS",length(AbsorbVIS)),
            rep("TransmVIS", length(TransmVIS)),
            rep("ReflecVIS", length(ReflecVIS)),
            rep("AbsorbNIR",length(AbsorbNIR)),
            rep("TransmNIR", length(TransmNIR)),
            rep("ReflecNIR", length(ReflecNIR))
            )) %>% 
  mutate(spp = substr(sppspot,1,7),
         spot = substr(sppspot,16,21),
         manip = substr(sppspot, 9, 14),
         band = substr(Oprop,7,9)) %>% 
  unite("SppTreat", spp, manip, sep="_", remove=FALSE) %>% 
  select(SppTreat , spot, value, Oprop, band, manip)


PivotBands$alpha <- ifelse(PivotBands$manip == "alterd", 0.5, 1)


PivotBands[PivotBands$SppTreat=="T.bruck_alterd",]
```

Now plot

```{r}
ggplot(PivotBands[PivotBands$spot=="bright",], 
       aes(x = SppTreat,
           y = value, fill = Oprop ,
           alpha = alpha)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Species", y = "Value") +
  #scale_fill_manual(values=c( "#4682B4", "#9ACD32","#FFA500"))+
  scale_alpha_identity() +  # Use identity scale for alpha
  coord_flip()+
  scale_fill_manual(values=c( "#4682B4","#4682B4",
                              "#9ACD32","#9ACD32", 
                              "#FFA500","#FFA500"))+
  facet_wrap(~band)+
  theme_minimal()

```

### Export data frame

```{r}
write.csv(PivotSun, here::here("Output/DataFrames/NIRVISOpticalProperties.csv"))
```


## midIR

```{r}
names(IRTra_Ely_pivot) <- c("spp", "pAUCTr", "bbTemp")
names(IRRef_Ely_pivot ) <- c("spp", "pAUCRf", "bbTemp")

Consolidated <- inner_join(IRTra_Ely_pivot, IRRef_Ely_pivot ,
                           by=c("spp","bbTemp")) %>% 
  mutate(AUCTr = 1-pAUCTr,
         AUCRf = 1-pAUCRf, 
         Emiss = 1- (AUCTr + AUCRf)) %>% 
  select(spp, bbTemp, AUCTr,AUCRf, Emiss)

PivotCon <- Consolidated %>% 
  gather(Measurement, ElyResponse, -spp, -bbTemp)

unique(PivotCon$bbTemp)

```



Plots

293K
```{r}
pospos <- c("Tbruck","Tbonvo", "Csexpl" , "Crayne", "Coctos", 
            "Elampr", "Aparvu", "Aaureu", "Aopali", "Alaetu") #define order

ggplot(PivotCon[PivotCon$bbTemp=="293bb",], 
       aes(x = factor(spp, levels =pospos),
           y = ElyResponse, fill = Measurement)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Species", y = "Value", fill = "Variable") +
  scale_fill_manual(values=c( "#FFA500", "#9ACD32", "#4682B4"))+
  coord_flip()+
  geom_hline(yintercept = 0.91, lty=2)+
  theme_minimal()

PivotCon[PivotCon$bbTemp=="293bb" &
         PivotCon$Measurement=="Emiss",]
```

```{r}
ggplot(PivotCon[PivotCon$bbTemp=="343bb",], 
       aes(x = factor(spp, levels =pospos),
           y = ElyResponse, fill = Measurement)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Species", y = "Value", fill = "Variable") +
  scale_fill_manual(values=c( "#FFA500", "#9ACD32", "#4682B4"))+
  coord_flip()+
  geom_hline(yintercept = 0.91, lty=2)+
  theme_minimal()

PivotCon[PivotCon$bbTemp=="343bb" &
         PivotCon$Measurement=="Emiss",]
```

### Export data frame

```{r}
write.csv(PivotCon, here::here("Output/DataFrames/midIRproperties.csv"))
```

